Project 1 for Complex Adaptive Systems

### 2018-02-20 paper.tex
fixed typo

\subsection{Additional Analysis}
\noindent Here we continue our exploration of the relationship between local and global population dynamics. We will use the metric displayed in Figure \ref{te_avg} $T_{M\rightarrow X} - T_{X\rightarrow M}$ to discuss the direction of causal inforamtion transfer between the two scales. We break our discussion into 3 cases.
\begin{itemize}
\item[i)] For small values of the global coupling strength, say $\epsilon < 0.3$, Figure \ref{te_avg} shows that our metric takes negative values. This indicates that causal information is flowing from the local to the global scale. The top row of Figure \ref{timeseries} shows that the individual population is chaotic, but the mean trajectory oscilates roughly between 3 values ($0.4$, $0.6$ and $0.6$). This is what gives the red points their behavior in Figure \ref{prettypicture}.
\item[ii)] For $\epsilon \approx 0.3$, the system synchronizes. In fact, we can compute the correlation between the trajectories in the middle row of Figure \ref{timeseries}, and see that it is nearly equal to one (0.9879)$. Based on Figure \ref{prettypicture} we sould expect these series to oscillate between precisely two values. This particular run had four attractors (black stars) instead of two.
\item[iii)] For large values of the global coupling strength, the global dynamics begin to dominate. There is still a near perfect correlation between $M$ and $X$, but now even the global dynamics (the mean) behaves chaotically.
\end{itemize}
For small values of the Global Coupling Strength, say $\epsilon < 0.3$, this metric takes negative values, indicating that information is flowing from the local to the global scale. The top row of Figure \ref{timeseires} shows that the individual populations appear chaotic, but the mean trajectory appears periodic. This is similar to the behavior illus

>>>>

\subsection{Additional Analysis}
\noindent Here we continue our exploration of the relationship between local and global population dynamics. We will use the metric displayed in Figure \ref{te_avg} $T_{M\rightarrow X} - T_{X\rightarrow M}$ to discuss the direction of causal inforamtion transfer between the two scales. We break our discussion into 3 cases.
\begin{itemize}
\item[i)] For small values of the global coupling strength, say $\epsilon < 0.3$, Figure \ref{te_avg} shows that our metric takes negative values. This indicates that causal information is flowing from the local to the global scale. The top row of Figure \ref{timeseries} shows that the individual population is chaotic, but the mean trajectory oscilates roughly between 3 values ($0.4$, $0.6$ and $0.6$). This is what gives the red points their behavior in Figure \ref{prettypicture}.
\item[ii)] For $\epsilon \approx 0.3$, the system synchronizes. In fact, we can compute the correlation between the trajectories in the middle row of Figure \ref{timeseries}, and see that it is nearly equal to one ($0.9879)$. Based on Figure \ref{prettypicture} we sould expect these series to oscillate between precisely two values. This particular run had four attractors (black stars) instead of two.
\item[iii)] For large values of the global coupling strength, the global dynamics begin to dominate. There is still a near perfect correlation between $M$ and $X$, but now even the global dynamics (the mean) behaves chaotically.
\end{itemize}
For small values of the Global Coupling Strength, say $\epsilon < 0.3$, this metric takes negative values, indicating that information is flowing from the local to the global scale. The top row of Figure \ref{timeseires} shows that the individual populations appear chaotic, but the mean trajectory appears periodic. This is similar to the behavior illus
